Adopting agile in the large: motivations, success factors and challenges

### 2013-12-20 journal/article.tex
Coding test

>>>>

\subsection{Validation of coding}

Before proceeding with the synthesis we conducted an experiment with the goal to
reveal the objectiveness of the coding by examining the amount of difference the
codings of two independent researchers may have. In the experiment Dikert and
Paasivaara coded independently a sample of five primary documents. The sample
was hand picked to present a representative subset of the source material. The
coding was done relying only on the above guidelines, and the researchers were
careful not to discuss the choice of codes or interpretations relating to codes
before the experiment was completed. Finally the independent codings of the two
researchers were analyzed with two metrics: by the number of matching themes
found, and by the amount of overlap in quotations similar codes have.

The metric of matching themes measures how well the independent researchers are
able to induct similar codes from the source material. As codes are inducted it
is likely that two researchers label similar quotes differently. To overcome
this problem we defined higher level themes under which the individual codes
were organized. Through discussion we made decisions on whether differently
labeled codes could be organized under the same theme or not. Table
\ref{table:codingexperiment} presents the total number of themes the researchers
found in each document, and how many of the themes were matching. We concluded
that on average two of three themes that one researcher finds are similarly
found by the other researcher, but one of three themes are not found by the
other researcher.

\begin{table}[h]
    \begin{tabular}{ l r r r }
        \toprule
        Document    &  Matching themes  &  Total themes  &  Quotation overlap (0-3) \\
        \midrule
        P1          &  14  &  19   &  2.1  \\
        P2          &   6  &  11   &  2.4  \\
        P3          &   7  &  11   &  2.1  \\
        P4          &   2  &   4   &  2.3  \\
        P5          &  12  &  16   &  2.0  \\
        \bottomrule
    \end{tabular}
    \caption{Result of independent coding experiment}
    \label{table:codingexperiment}
\end{table}
